Dual terminal sliding mode control

### 2016-05-14 paper3_manuscript.tex
20160514

For verifying the effectiveness of the DSM control scheme, consider the following four-order nonlinear system with the disturbance:

@@

\dot x_4 &= 0.3\sin(3t)+0.5e^{-3t}+u_2,

@@

@@

>>>>

For verifying the effectiveness of the proposed control scheme, consider the following four-order nonlinear system with the disturbance:

@@

\dot x_4 &= 0.3\sin(3t)+0.5e^{-3t}+u_2,\label{eq:simulation four order system}

@@

and one can produce a DSM control scheme conveniently. It is obvious that the disturbance in the system~(\ref{eq:simulation four order system}) behaves bounded, which is said to be the following uncertainty terms:
\Vert g_1(x,t)\Vert &= \Vert 0.1\sin(20t)\Vert\le 0.1\\
\Vert g_2(x,t)\Vert &= \Vert 0.3\sin(3t)+0.5e^{-3t}\Vert\le 0.8,
and hence, based on the analysis in Theorem~\ref{theorem:1}, $\eta_1>0.1$ and $\eta_2>0.8$ can be determined accordingly to guarantee the reaching condition of the desired sliding manifold. Also, the inputs $u_1$ and $u_2$ are able to be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation four order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.

@@

In order to evaluate the performance of the proposed control scheme, a simulation about the $2$-link robot manipulator is presented in the following. The dynamics of this manipulator can be explained by the dynamic equations in following forms:
\begin{bmatrix}
m_{12}(q_2) &m_{12}(q_2)\\
m_{21}(q_2) &m_{22}
\end{bmatrix}
\ddot q_1\\
\ddot q_2
+
\begin{bmatrix}
-c(q_2)\dot q_1^2-2c(q_2)\dot q_1\dot q_2\\
c(q_2)\dot q_2^2
\end{bmatrix}+
\begin{bmatrix}
\xi_1(q_1,q_2) g\\
\xi_2(q_1,q_2) g
\end{bmatrix}=
\tau_1\\
\tau_2
\end{pmatrix},
&m_{11}(q_2)=(m_1+m_2)r_1^2+m_2r_2^2+2m_2r_1r_2\cos(q_2)+J_1,\\
&m_{12}(q_2)=m_2r_2^2+m_2r_1r_2\cos(q_2),\\
&m_{21}(q_2)=m_{12}(q_2),\\
&m_{22}=m_2r_2^2+J_2,\\
&c(q_2)=m_2r_1r_2\sin(q_2),\\
&\xi_1(q_1,q_2) =((m_1+m_2)r_1\cos(q_2)+m_2r_2\cos(q_1+q_2)),\\
&\xi_2(q_1,q_2) = m_2r_2\cos(q_1+q_2).
